---
title: "Untitled"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r warning=FALSE, message=FALSE}
library(tidyverse)
library(janitor)
library(lubridate)
library(scales)
library(readxl)
library(stargazer)
library(ggrepel)
theme_set(theme_classic())
options(scipen = 100)

## Data Load
covid_owid_raw <- read_csv("https://covid.ourworldindata.org/data/owid-covid-data.csv")
covid_stringency_raw <- read_csv("covid-stringency-index.csv") %>% clean_names()
oxcovid_raw <- read_csv("https://raw.githubusercontent.com/OxCGRT/covid-policy-tracker/master/data/OxCGRT_latest.csv")
covid_coronanet_raw <- read_csv("coronanet_release.csv")
gdi_raw <- read_csv("f236b9a8-c325-4bf5-a685-86d3df7c8542_Data.csv") %>% clean_names()
polity_raw <- read_excel("p5v2018.xls")

```

## Read in and clean WGI

```{r}
gdi_cleaned <- gdi_raw %>% 
  filter(series_name == "Government Effectiveness: Estimate") %>% 
  mutate_at(vars(matches("^x")), as.numeric) %>% 
  pivot_longer(cols = x1996_yr1996: x2019_yr2019, names_to = "year", values_to = "gov_effectiveness") %>% 
  mutate(year = as.numeric(str_extract(year, "\\d...")))

gdi_cleaned %>% 
  filter(country_name == "China") %>% 
  ggplot(aes(year, gov_effectiveness)) +
  geom_line()

gdi_selected <- gdi_cleaned %>% 
  filter(year == 2019) %>% 
  select(country_name, country_code, gov_effectiveness)
```

## Load and clean PolityIV dataset

```{r}
polity_selected <- polity_raw %>% 
  filter(year == 2018) %>% 
  select(country, polity2, scode) %>% 
  mutate(country = recode(country,  
                          "Korea South" = "South Korea", 
                          "UAE" = "United Arab Emirates",
                          "Bosnia" = "Bosnia & Herzegovina",
                          "Congo Kinshasa" = "Congo - Kinshasa", 
                          "Congo Brazzaville" = "Congo - Brazzaville", 
                          "Cote D'Ivoire" = "Côte d’Ivoire", 
                          "Czech Republic" = "Czechia",
                          "Slovak Republic" = "Slovakia", 
                          "Sudan-North" = "Sudan", 
                          "Timor Leste" = "Timor-Leste",
                          "Trinidad and Tobago" = "Trinidad & Tobago", 
                          "Macedonia" = "North Macedonia"))
```

## Load and clean Economist Intelligence Unit Democracy Index

```{r}
eiu_democracy_index_raw <- read_excel("economist_intel_unit_democracy_index.xlsx") %>% clean_names()

eiu_overall_selected <- eiu_democracy_index_raw %>% 
  mutate(country = str_trim(country)) %>% 
  select(country, overall_score)
```


## Load and clean oxcovid dataset

```{r}
oxcovid_raw
```



## Core dataset: Load and clean owid-covid19-dataset

```{r}
covid_owid_joined <- covid_owid_raw %>%
  filter(!is.na(continent), 
         !is.na(total_deaths_per_million), 
         population > 1000000) %>% 
  left_join(gdi_selected, by = c("iso_code" = "country_code")) %>% 
  left_join(polity_selected, by = c("country_name" = "country")) %>% 
  mutate(death_rate = total_deaths / total_cases)

covid_owid_present <- covid_owid_joined %>% filter(date == "2021-06-01")
```

## Take a snapshot view of policy performance

```{r}
plot_variable <- function(tbl, day, column, column_2) {
  tbl %>% 
    filter(date == day) %>% 
    ggplot(aes({{ column }}, {{ column_2 }})) +
    geom_point(aes(size = total_deaths_per_million), alpha = .6) +
    geom_smooth(method = "lm") +
    scale_y_log10()
}

covid_owid_joined %>%
  plot_variable(day = "2021-05-01", column = gov_effectiveness, column_2 = death_rate) +
  geom_text_repel(data = country_df, aes(label = location), min.segment.length = 0, seed = 42, box.padding = 0.5) +
  labs(title = "Does government effectiveness matter?", 
       subtitle = "Government effectiveness and mortality rate", 
       x = "WGI (government effectiveness)", 
       y = "Mortality rate (death / confirmed case)", 
       caption = "Data Source: Our World in Data, Worldwide Governance Indicator") +
  theme(text = element_text(family = "Times"), 
        plot.title = element_text(face = "bold", 
                                  size = 15), 
        legend.position = "bottom")
ggsave(filename = "does_gov_effectiveness_matter.pdf", width = 8, height = 5)


covid_owid_joined %>% 
  plot_variable(day = "2021-05-01", column = stringency_index, column_2 = death_rate)

covid_owid_joined %>% 
  plot_variable(day = "2021-05-01", column = polity2, column_2 = death_rate)

covid_owid_joined %>% 
  plot_variable(day = "2021-05-01", value, stringency_index)
```


## Regression Analysis

```{r}
library(effects)
library(broom)

model_1 <- lm(data = covid_owid_present, log(death_rate) ~ log(population) + aged_65_older + log(gdp_per_capita) + hospital_beds_per_thousand + gov_effectiveness + stringency_index)

model_2 <- lm(data = covid_owid_present, log(death_rate) ~ log(population_density) + aged_65_older + log(gdp_per_capita) + hospital_beds_per_thousand + gov_effectiveness * polity2 + stringency_index)

model_3 <- lm(data = covid_owid_present, total_cases_per_million ~ log(population) + aged_65_older + gdp_per_capita + hospital_beds_per_thousand + gov_effectiveness * stringency_index) 

model_4 <- lm(data = covid_owid_present, total_cases_per_million ~ log(population) + aged_65_older + gdp_per_capita + hospital_beds_per_thousand + gov_effectiveness * stringency_index + polity2)

stargazer(model_1, model_2, model_3, model_4, type = "text")

effect(term = "gov_effectiveness", mod = model_2) %>% 
  plot(type = "response", ylim=c(0,1), main = "Gov_effectiveness")

model_2 %>% 
  tidy(conf.int = TRUE) %>% 
  filter(term != "(Intercept)") %>% 
  mutate(term = fct_reorder(term, -estimate)) %>% 
  ggplot(aes(term, estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high, width = .2)) +
  geom_hline(aes(yintercept = 0), color = "red", lty = "dashed") +
  coord_flip() +
  labs(title = "Does government effectiveness matter?", 
       subtitle = "Associations between different parameters and mortality rate", 
       y = "Percentage change in mortalilty rate associated with a one-unit increase \n in parameter indices", 
       x = " ", 
       caption = "Data Source: OxCGRT, WGI, OWID") +
  theme(text = element_text(family = "Times"), 
        plot.title = element_text(face = "bold", size = 15))
ggsave(file = "figs/does_government_effectiveness_matter.pdf", width = 8, height = 5)

```

## How well has China done?

```{r}
library(ggrepel)
library(ggforce)

country_df <- covid_owid_joined %>% 
  filter(date == "2021-05-01") %>%
  filter(location %in% c("China", "Taiwan", "Vietnam", "Singapore", "Thailand", "South Korea", "Japan", "United States","Russia", "Italy", "Mexico", "Burundi", "Tanzania"))

best_performers <- covid_owid_joined %>% 
  filter(date == "2021-05-01") %>%
  filter(location %in% c("China", "Taiwan", "Vietnam", "Tanzania"))

covid_owid_joined %>% 
  filter(date == "2021-05-01") %>%
  filter(death_rate < .15) %>% 
  ggplot(aes(total_cases_per_million, death_rate)) +
  geom_point() +
  # geom_smooth(method = "lm") +
  geom_text_repel(data = country_df, aes(label = location), position = position_jitter(),
                  min.segment.length = 0, seed = 42, box.padding = 0.5) +
  geom_mark_circle(data = best_performers, color = "red") +
  scale_x_log10() +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(title = "Fig 2. Total number of confirmed cases and mortality rate", 
       subtitle = "As of May 1, 2021",
       caption = "Data Source: Our World in Data", 
       x = "Total cases per million (log)", 
       y = "Mortality rate (%)") +
  theme(text = element_text(family = "Times"), 
        plot.title = element_text(face = "bold", size = 12)) 
ggsave(filename = "figs/total_cases_mortality_rate.pdf", width = 8, height = 4)

```

## Trend in the number of new cases

```{r}
covid_owid_joined %>% 
  filter(location %in% c("China", "Japan", "United States")) %>% 
  ggplot(aes(date, new_cases, lty = location)) +
  geom_line() +
  scale_y_log10(labels = comma) +
  scale_x_date(date_breaks = "2 month", 
               date_labels = "%y-%m", 
               expand = c(0, 0)) +
  labs(title = "Fig 1. Comparing the trend in the daily total of confirmed cases",
       subtitle = "The number of new cases in China has fallen below 50 per day since Feb 2021",
       x = NULL, 
       y = "Daily total of confirmed cases (log)",
       caption = "Data Source: Our World in Data") +
  theme(text = element_text(family = "Times", size = 12), 
        plot.title = element_text(face = "bold"), 
        legend.position = "bottom", 
        legend.title = element_blank())
ggsave(filename = "figs/comparing_trend_number_of_new_cases.pdf", width = 8, height = 4)

covid_owid_joined %>% 
  filter(location == "China") %>% 
  filter(date < "2021-01-01") %>% 
  group_by(month(date)) %>% 
  summarize(n = n(), 
            avg_cases = sum(new_cases, na.rm = T) / n)

covid_owid_joined %>% 
  filter(location == "Vietnam", 
         date == "2021-05-01")
```

## Stringency trend 

```{r}
covid_owid_joined %>% 
  ggplot(aes(stringency_index)) +
  geom_histogram() 

stringency_index_filtered <- covid_owid_joined %>% 
  filter(date > "2020-03-31", 
         !is.na(stringency_index)) %>% 
  group_by(location) %>% 
  summarize(avg_stringency = mean(stringency_index))

stringency_index_filtered %>% 
  filter(date == "2020-05-01") %>% 
  ggplot(aes(gov_effectiveness, avg_stringency)) +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_text_repel(data = country_df, aes(label = location), min.segment.length = 0, seed = 42, box.padding = 0.5) +
  scale_x_log10() 

```

## Coronanet China 

```{r}
coronanet_china <- covid_coronanet_mutated %>% 
  filter(country == "China")

coronanet_china %>% 
  ggplot(aes(date_announced)) +
  geom_histogram()

coronanet_china %>% 
  count(init_country_level, sort = TRUE)

coronanet_china %>% 
  count(compliance, sort = T)

coronanet_china %>% 
  count(province, sort = T)

coronanet_china %>% 
  #count(province, type, compliance) %>% 
  filter(province == "Henan", 
         type == "Declaration of Emergency")


```

## Stringency index

```{r}
covid_stringency_raw %>% 
  filter(entity %in% c("China", "Vietnam", "Taiwan")) %>% 
  mutate(entity = fct_relevel(entity, "China", "Vietnam", "Taiwan")) %>% 
  ggplot(aes(day, stringency_index, lty = entity)) + 
  geom_line(size = .65) +
  scale_x_date(date_breaks = "2 months", 
               date_labels = "%Y-%m", 
               expand = c(0, 9)) +
  labs(title = "Fig 3. Comparing the stringency level of crisis responses", 
       subtitle = "China as a case of high-pressure and high-effect", 
       x = " ", 
       y = "Stringency index", 
       caption = "Data Source: Oxford Covid Government Response Tracker (OxCGRT)") +
  theme(text = element_text(family = "Times"),
        plot.title = element_text(face = "bold", size = 12),
        legend.position = "bottom", 
        legend.title = element_blank(), 
        )
ggsave(filename = "figs/comparing-stringency-of-crisis-response.pdf", width = 8, height = 4)

oxcovid_raw %>% 
  filter(country_name %in% c("China", "Vietnam", "Taiwan", "Tanzania", "Russia")) %>% 
  mutate(country_name = fct_relevel(country_name, "China", "Vietnam", "Tanzania", "Taiwan", "Russia")) %>% 
  ggplot(aes(date, stringency_index, color = country_name)) + 
  geom_line(size = .65) +
  scale_x_date(date_breaks = "2 months", 
               date_labels = "%Y-%m", 
               expand = c(0, 9)) +
  labs(title = "Figure 3. Comparing the stringency level of crisis responses", 
       subtitle = "China as a case of high-pressure and high-effect measures", 
       x = " ", 
       y = "Stringency index", 
       caption = "Data Source: Oxford Covid Government Response Tracker (OxCGRT)") +
  theme(text = element_text(family = "Times"),
        plot.title = element_text(face = "bold", size = 15),
        legend.position = "bottom", 
        legend.title = element_blank(), 
        )

```


```{r}
covid_stringency_raw %>% 
  count(entity, sort = T)

sars_mers_countries <- c("Taiwan", "Singapore", "Canada", "China", "Hong Kong", "Vietnam", "United States", "United Arab Emirates", "South Korea", "Saudi Arabia")

covid_stringency_raw$sars_mers_50 <- ifelse(covid_stringency_raw$entity %in% sars_mers_countries, 1, 0)

covid_stringency_raw %>% 
  filter(sars_mers_50 == 1) 
```




